Age-related changes in plant growth and traits

### 2016-06-01 scripts/Accessory_figs_20160218.Rmd
work on accessory figs

#Table 1 showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp <- format(acc_costs_spp, digit=2)

@@

#Figure 2. Ternary diagram showing seed_costs
```{r}
ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs_corr)
ternary$pack_disp_costs_corr[9] <- 0.1

ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs_corr
ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
ternary$post_poll <- 100-ternary$per_poll
ternary$per_seed <-100*ternary$seed_size/ternary$seed_costs
ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs

@@

#Figure 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_seed_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

#Figure 3 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
slopes <- sma(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

@@

plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="EPMI"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
slopes <- sma(packaging_dispersal_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="EPMI"),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="embryo + endosperm size (mg)",side=1,line=1.5,outer=TRUE)

@@

#Figure 4 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
```{r}
win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
plot

@@

#Figure 4, using embryo + endosperm
```{r}

win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
plot

@@

plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
sma_abline(mod)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")

@@

#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
plot(scaled_seed_count~embryo_endo_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)

@@

xvar <- "seedset"
yvar <- "packaging_dispersal_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

>>>>

#Table 1 showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,pack_disp_costs,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp <- format(acc_costs_spp, digit=2)

@@

#Figure 2. Ternary diagram showing seed_costs
```{r}
ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs)
ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs

ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
ternary$post_poll <- 100-ternary$per_poll
ternary$per_seed <-100*ternary$seed_size/ternary$seed_costs
ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs

@@

#Figure 4. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

#Figure 4 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
slopes <- sma(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

@@

plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
slopes <- sma(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="embryo + endosperm size (mg)",side=1,line=1.5,outer=TRUE)

@@

#Figure 5 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
```{r}
win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
plot

@@

#Figure 5, using embryo + endosperm
```{r}

win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
plot

@@

plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,100),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="embryo + endosperm size (mg)",ylab="seed set")
mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
sma_abline(mod)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
text((10^(0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),(10^(0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")

@@

#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
plot(scaled_seed_count~embryo_endo_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,100),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="embryo + endosperm size (mg)",ylab="count, scaled to plant size")
points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)

@@

xvar <- "seedset"
yvar <- "pack_disp_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
